---
title: "Final Project Quarto"
format: html
editor: visual
---

## Quarto

```{r}
install.packages("here")
library(here)

survivalists <- here("C:\Users\fizza\Downloads\Emory Rollins\Summer 2023\EPI 590R R bootcamp\epi590r-in-class\590R-Final-Project\survivalists.rda")
```

```{r}
#| echo: false
#| label: tbl-one
#| tbl-cap: "Descriptive statistics of survivalists"
library(gtsummary)
table1 <- tbl_summary(survivalists,
						by = gender,
						include = c(age, days_lasted,
												result)
)
table1
```

```{r}
#| echo: false
#| label: tbl-two
#| tbl-cap: "Regression Table"
table2 <- tbl_uvregression(survivalists,
								 x = gender,
								 include = c(age, days_lasted, result),
								 label = list(
								 	age ~ "Age",
								 	days_lasted ~ "Days Lasted",
								 	result ~ "Result"),
								 method = lm)
table2
```

```{r}
#| echo: false
#| label: fig-one
#| tbl-cap: "Histogram of Days Lasted"
fig1 <- hist(survivalists$days_lasted)
fig1
```

```{r}
gtsummary::inline_text(table2, variable = "age")
lasted_f <- inline_text(table1, variable = "days_lasted", column = "Female")
lasted_m <- inline_text(table1, variable = "days_lasted", column = "Male")
```

The regression table shows the relationship between gender and the outcome variables of age, days lasted on the show, and result of place finished. @tbl-one shows additional descriptive statistics on these variables. @fig-one displays the distribution of days lasted across the survivalists. A greater proportion of female (`r lasted_f`) than male (`r lasted_m`) survivalists lasted over 40 days.
